\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{left=1.25cm, top=1.25cm, right=1.25cm, bottom=1.25cm}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\begin{document}

\centerline{\Huge \textbf{Andrew}}
\vspace{0.2cm}
\centerline{todrewmailbox@email.com | +62 882 1306 1984 | Jakarta, Indonesia}
\centerline{github.com/drewhub88}

\vspace{0.5cm}
  
\section*{PROFESSIONAL SUMMARY}
\hrule
\vspace{0.2cm}
 A multi-skilled professional with a strong background in e-commerce operations, web development, and creative production. Experience ranges from managing daily production teams to implementing custom web solutions and running digital marketing campaigns.

\vspace{0.4cm}

\section*{TECHNICAL \& CORE SKILLS}
\hrule
\vspace{0.2cm}
\textbf{Leadership \& Operations:} Team Leadership, Production Supervision, Operations Management, Project Coordination, Technical Consulting \\
\textbf{Backend \& Web Development:} Python, C++, PHP, JavaScript, SQL, WordPress, API Integration, LaTeX \\
\textbf{Digital \& Design:} Meta Ads Analysis, Digital Illustration, Visual Content Creation, Brand Identity, Product Retouching \\
\textbf{Business:} E-commerce Management, Bookkeeping, Business Administration

\vspace{0.4cm}

\section*{WORK EXPERIENCES}
\hrule
\vspace{0.3cm}

\textbf{General Operation Manager} \hfill 2021 -- 2023 \\
\textit{Women's Fashion Brand} \hfill Jakarta, Indonesia
\begin{itemize}[noitemsep, topsep=0pt]
    \item Optimising layout and presentation of the offline and e-commerce storefronts to improve customer experience and increase conversion rates.
    \item Ran and analyse digital marketing campaigns, utilising data insights to optimise ad budget.
    \item Oversaw day-to-day operations across social media channels and e-commerce marketplaces to ensure consistent performance.
\end{itemize}

\vspace{0.4cm}

\noindent\textbf{Web Developer \& Consultant (Freelance)} \hfill 2019 -- Present
\begin{itemize}[noitemsep, topsep=0pt]
    \item Managed end-to-end delivery of custom CMS solutions, coordinating directly with clients to define project scopes and timelines.
    \item Engineered secure backend architectures, integrating payment gateways and third-party APIs to support various e-commerce models.
\end{itemize}

\vspace{0.4cm}

\noindent\textbf{Illustrator, Visual Designer \& Consultant (Freelance)} \hfill 2016 -- Present
\begin{itemize}[noitemsep, topsep=0pt]
    \item Produced custom digital illustrations for merchandise and visual content to elevate client branding across social media and digital storefronts.
    \item Managed end-to-end creative projects, advising businesses on brand identity while delivering cohesive style guides and logos.
\end{itemize}

\vspace{0.4cm}

\noindent\textbf{Production Team \& Supervisor} \hfill 2018 -- 2020 \\
\textit{Private Printing Company} \hfill Jakarta, Indonesia
\begin{itemize}[noitemsep, topsep=0pt]
    \item Directed production staff and monitored daily output to ensure strict shipping deadlines.
    \item Managed quality control and optimised printing film materials for cost-effectiveness.
\end{itemize}

\vspace{0.4cm}

\section*{PERSONAL PROJECTS}
\hrule
\vspace{0.2cm}
\textbf{Automated Resume Pipeline} | \textit{LaTeX, YAML, GitHub Actions}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a CI/CD pipeline that automatically compiles LaTeX source code into a professional PDF on every commit.
\end{itemize}

\vspace{0.3cm}

\section*{EDUCATION}
\hrule
\vspace{0.2cm}
\textbf{Senior Vocational School (SMK)} \hfill 2016 \\
\textit{Major in Software Engineering (Rekayasa Perangkat Lunak)} \hfill Jakarta, Indonesia

\end{document}